### 2020-02-29 Thesis-Chapter3-Arguments.tex
Add \my{chap/sec/fig/tab} commands

In this chapter, develop the arguments introduced in \ref{sec-argsbackground}. Make use of argument maps to break down
and visualize the debate, as shown in \Figure~\fref{fig-args-top-level}.

>>>>

In this chapter, develop the arguments introduced in \mysec{sec-argsbackground}. Make use of argument maps to break down
and visualize the debate, as shown in \myfig{fig-args-top-level}.
